From Questions to Queries – Enhancing the Curt System by a Theory and Implementation of Embedded WH-Questions

### 2008-09-01 thesis/paper.tex
removed footnote about holesem

In order to cope with more complicated quantifier configurations, where
constraints need to be enforced, and with other kinds of ambiguities,
Blackburn and Bos present an approach utilizing underspecified representations and
dominance relations, \pn{Hole Semantics}\footnote{Also presented in % todo:cite
%Bos' paper
}. 
However none of the cases discussed so far would require the enhanced
expressive power of \pn{Hole Semantics} it was decided to not change the \curt{}
implementation's current architecture which employs \pn{Keller Storage}.

>>>>

In order to cope with more complicated quantifier configurations, where
constraints need to be enforced, and with other kinds of ambiguities,
Blackburn and Bos present an approach utilizing underspecified representations and
dominance relations, \pn{Hole Semantics}.
However, none of the cases discussed so far would require the enhanced
expressive power of \pn{Hole Semantics} it was decided to not change the \curt{}
implementation's current architecture which employs \pn{Keller Storage}.
